Delayed effects of [responses to?] climate lead to demographic divergence in a fragmented Amazonian landscape

### 2021-05-11 doc/paper.Rmd
create stand-alone plot of survivorship curve

```{r load-targets}
withr::with_dir(here(), {
  tar_load(c(
    eda_plot,
    s_spei_plot,
    g_spei_plot,
    f_spei_plot,
    size_plot,
    f_cf,
    f_1ha,
    model_data,
    xa_spei
  ))
})
```

@@

>>>>

```{r load-targets}
withr::with_dir(here::here(), {
  tar_load(c(
    eda_plot,
    surv_curve,
    s_spei_plot,
    g_spei_plot,
    f_spei_plot,
    size_plot,
    f_cf,
    f_1ha,
    model_data,
    xa_spei
  ))
})
```

@@

```{r}
surv_curve_cap <- "Survivorship of plants labeled in the first survey year, 1998, which comprise 49% of the plants in the full dataset. After 10 years, 79.7% (1629/2055) of plants in continuous forest survived and 72.4% (393/543) of plants in fragments survived."
```

```{r surv_curve, fig.cap=surv_curve_cap, fig.width=7, fig.height=3.5}
surv_curve + theme(text = element_text(size = 10))
```
